---
title: "Topic 2: Text Data in R"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Connect to the New York Times API and send a query

```{r load-packages}
library(jsonlite) #convert results from API queries into R-friendly formats 
library(tidyverse)
library(tidytext)
library(ggplot2)
```

```{r api, eval = FALSE}
#create an object called x with the results of our query ("haaland")

class(x) #what type of object is x?

#flatten the JSON object, then convert to a data frame
x <- fromJSON("http://api.nytimes.com/svc/search/v2/articlesearch.json?q=haaland&api-key=NTKBHbsb6XFEkGymGumAiba7n3uBvs8V", flatten = TRUE) %>% #the string following "key=" is the 
  data.frame()

#Inspect our data
class(x) #now what is it?
dim(x) # how big is it?
names(x) # what variables are we working with?
saveRDS(x, "initquery.RDS")
x <- readRDS("nytDat.rds")
#response.xxx.xxx... is legacy of the json nested hierarchy
```

### OK, it's working but we want more data. Let's set some parameters

```{r}
term <- "Haaland" # Need to use + to string together separate words
begin_date <- "20210120"
end_date <- "20220401"

baseurl <- paste0("http://api.nytimes.com/svc/search/v2/articlesearch.json?q=",term,
                  "&begin_date=",begin_date,"&end_date=",end_date,
                  "&facet_filter=true&api-key=","NTKBHbsb6XFEkGymGumAiba7n3uBvs8V", sep="")

#examine our query url
baseurl
```

```{r, eval=FALSE}
 initialQuery <- fromJSON(baseurl)
maxPages <- round((initialQuery$response$meta$hits[1] / 10)-1) 

pages <- list()
for(i in 0:maxPages){
  nytSearch <- fromJSON(paste0(baseurl, "&page=", i), flatten = TRUE) %>% data.frame() 
  message("Retrieving page ", i)
  pages[[i+1]] <- nytSearch 
  Sys.sleep(1) 
}
class(nytSearch)

nytDat <- rbind_pages(pages)
nytDat <- as_tibble(nytDat)

```

```{r article-type}
nytDat <- read.csv("nytDat.csv")

nytDat %>% 
  group_by(response.docs.type_of_material) %>%
  summarize(count=n()) %>%
  mutate(percent = (count / sum(count))*100) %>%
  ggplot() +
  geom_bar(aes(y=percent, x=response.docs.type_of_material, fill=response.docs.type_of_material), stat = "identity") + coord_flip()
```

```{r date-plot}
nytDat %>%
  mutate(pubDay=gsub("T.*","",response.docs.pub_date)) %>%
  group_by(pubDay) %>%
  summarise(count=n()) %>%
  filter(count >= 2) %>%
  ggplot() +
  geom_bar(aes(x=reorder(pubDay, count), y=count), stat="identity") + coord_flip()
```

```{r}
#The 6th column, "response.doc.lead_paragraph", is the one we want here
names(nytDat)
paragraph <- names(nytDat)[6]
tokenized <- nytDat %>%
  unnest_tokens(word, paragraph)

tokenized %>%
  count(word, sort = TRUE) %>%
  filter(n > 50) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word)) +
  geom_col() +
  labs(y = NULL)

data(stop_words)

tokenized <- tokenized %>%
  anti_join(stop_words)

tokenized %>%
  count(word, sort = TRUE) %>%
  filter(n > 5) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word)) +
  geom_col() +
  labs(y = NULL)
```

```{r cleaning}
#inspect the list of tokens (words)
tokenized$word

clean_tokens <- str_replace_all(tokenized$word,"trib[a-z,A-Z]*","tribe") #stem tribe words
clean_tokens <- str_remove_all(clean_tokens, "[:digit:]") #remove all numbers
clean_tokens <- gsub("’s", '', clean_tokens)


```
1. Create a free New York Times account (https://developer.nytimes.com/get-started)

2. Pick an interesting environmental key word(s) and use the jsonlite package to query the API.  Pick something high profile enough and over a large enough time frame that your query yields enough articles for an interesting examination.

3. Recreate the publications per day and word frequency plots using the first paragraph
 - Make some (at least 3) transformations to the corpus (add stopword(s), stem a key term and its variants, remove numbers)
  
4. 

```{r assignment}



```







