---
title: "Topic 4: Sentiment Analysis II"
---

This .Rmd available here: <https://raw.githubusercontent.com/MaRo406/EDS_231-text-sentiment/main/topic_4.Rmd>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### IPCC Report Twitter

```{r packages, results='hide', message=FALSE, warning=FALSE}
library(quanteda)
library(tidyverse)
library(tidytext)
library(lubridate)
#devtools::install_github("quanteda/quanteda.sentiment") #not available currently through CRAN
library(quanteda.sentiment)
library(wordcloud) #visualization of common words in the data set
library(reshape2)
```

Last week we used the tidytext approach to sentiment analysis for Nexis Uni .pdf data on coverage of the recent IPCC report. This week we will look at the conversation on Twitter about the same report. We'll start with the familiar tidy approach, and then introduce the quanteda package later.

```{r tweet_data}

raw_tweets <- read.csv("https://raw.githubusercontent.com/MaRo406/EDS_231-text-sentiment/main/dat/IPCC_tweets_April1-10_sample.csv", header=TRUE)

dat<- raw_tweets[,c(5,7)] # Extract Date and Title fields

tweets <- tibble(text = dat$Title,
                  id = seq(1:length(dat$Title)),
                 date = as.Date(dat$Date,'%m/%d/%y'))


head(tweets$text, n = 10)

#simple plot of tweets per day
tweets %>%
  count(date) %>%
  ggplot(aes(x = date, y = n))+
  geom_line()

```

```{r cleaning_tweets}

#let's clean up the URLs from the tweets
tweets$text <- gsub("http[^[:space:]]*", "",tweets$text)
tweets$text <- str_to_lower(tweets$text)

#load sentiment lexicon
bing_sent <- get_sentiments('bing')

#tokenize tweets to individual words
words <- tweets %>%
  select(id, date, text) %>%
  unnest_tokens(output = word, input = text, token = "words") %>%
  anti_join(stop_words, by = "word") %>%
  left_join(bing_sent, by = "word") %>%
  left_join(
    tribble(
      ~sentiment, ~sent_score,
      "positive", 1,
      "negative", -1),
    by = "sentiment")
```

```{r sentiment_calculations}
#take average sentiment score by tweet
tweets_sent <- tweets %>%
  left_join(
    words %>%
      group_by(id) %>%
      summarize(
        sent_score = mean(sent_score, na.rm = T)),
    by = "id")

neutral <- length(which(tweets_sent$sent_score == 0))
positive <- length(which(tweets_sent$sent_score > 0))
negative <- length(which(tweets_sent$sent_score < 0))

Sentiment <- c("Positive","Neutral","Negative")
Count <- c(positive,neutral,negative)
output <- data.frame(Sentiment,Count)
output$Sentiment<-factor(output$Sentiment,levels=Sentiment)
ggplot(output, aes(x=Sentiment,y=Count))+
  geom_bar(stat = "identity", aes(fill = Sentiment))+
  scale_fill_manual("legend", values = c("Positive" = "green", "Neutral" = "black", "Negative" = "red"))+
  ggtitle("Barplot of Sentiment in IPCC tweets")
```

```{r plot_sentiment_by_day}
# tally sentiment score per day
daily_sent <- tweets_sent %>%
  group_by(date) %>%
  summarize(sent_score = mean(sent_score, na.rm = T))

daily_sent %>%
  ggplot( aes(x = date, y = sent_score)) +
  geom_line() +
    labs(x = "Date",
    y = "Avg Sentiment Score",
    title = "Daily Tweet Sentiment",
    subtitle = "IPCC Tweets")

```

Now let's try a new type of text visualization: the wordcloud.

```{r wordcloud}
words %>%
   anti_join(stop_words) %>%
   count(word) %>%
   with(wordcloud(word, n, max.words = 200))
```

```{r wordcloud_comp}

words %>%
inner_join(get_sentiments("bing")) %>%
count(word, sentiment, sort = TRUE) %>%
acast(word ~ sentiment, value.var = "n", fill = 0) %>%
comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)
```

#### The quanteda package

quanteda is a package (actually a family of packages) full of tools for conducting text analysis. quanteda.sentiment (not yet on CRAN, download from github) is the quanteda modular package for conducting sentiment analysis.

quanteda has its own built in functions for cleaning text data. Let's take a look at some. First we have to clean the messy tweet data:

```{r create_corpus}
corpus <- corpus(dat$Title) #enter quanteda
summary(corpus)
```

```{r quanteda_cleaning}
tokens <- tokens(corpus) #tokenize the text so each doc (page, in this case) is a list of tokens (words)

#examine the uncleaned version
tokens

#clean it up
tokens <- tokens(tokens, remove_punct = TRUE,
                      remove_numbers = TRUE)

tokens <- tokens_select(tokens, stopwords('english'),selection='remove') #stopwords lexicon built in to quanteda

#tokens <- tokens_wordstem(tokens) #stem words down to their base form for comparisons across tense and quantity

tokens <- tokens_tolower(tokens)

```

we can use the kwic function (keywords-in-context) to briefly examine the context in which certain words appear.

```{r initial_analysis}
head(kwic(tokens, "climate", window = 3))

```

```{r}

dfm <- dfm(tokens)

topfeatures(dfm, 12)

dfm.sentiment <- dfm_lookup(dfm, dictionary = data_dictionary_LSD2015)

head(textstat_polarity(tokens, data_dictionary_LSD2015))


```

### Assignment

You will use the tweet data from class today for each part of the following assignment.

1.  Think about how to further clean a twitter data set. Let's assume that the mentions of twitter accounts is not useful to us. Remove them from the text field.

2.  Create a [grouped barplot](https://www.statology.org/grouped-barplot-in-r/#:~:text=A%20grouped%20barplot%20is%20a,the%20data%20visualization%20library%20ggplot2.) that plots the number of positive, negative and neutral tweets per day.

3.  Adjust the wordcloud in the "wordcloud" chunk by coloring the positive and negative words so they are identifiable.
